### 2019-02-18 sections/intuition.tex
basic buliding blocks

This section gives an overview of the core concepts of task oriented programming (\TOP).

@@

The central objective of \TOP is to \emph{coordinate collaboration}.
To this end, \TOPHAT has basic tasks called editors, with which users can
interact, and combinators to express ways in which people can work together.
Tasks can be executed after each other, at the same time, or
conditionally. This motivates the task combinators for steps, parallel
combination, and choice.
%One can say that tasks are a way to model \emph{workflows}.
% \TOPHAT is a language to specify workflows.

>>>>

This section gives an overview over the core concepts of task-oriented programming.

@@

The central objective of \TOP is to \emph{coordinate collaboration}.
The basic building blocks of \TOPHAT are editors and combinators.
Editors are tasks with which users interact directly.
Combinators express ways in which people can work together.
Tasks can be executed after each other, at the same time, or conditionally.
This motivates the combinators step, parallel, and choice.
